---
title: "Dissertation Supplemental Analyses"
author: "Steven T. Tseng"
date: '`r paste("First created on April 4, 2020. Updated on", Sys.Date())`'
output: 
  html_notebook:
    theme: cerulean
    highlight: tango
    number_sections: yes
    toc: yes
---

```{r, message = FALSE}
library(dplyr)
library(readxl)
library(psych)
library(lattice)
library(ggplot2)
library(lavaan)
library(magrittr)
library(broom)

options(digits = 3)
theme_set(theme_classic())

dat <- read_xlsx("./Dissertation Data/dissertationdataCOMPLETE.xlsx")
```

****

# Regressions with Controls

* Present regression results to bolster correlation results
* Include demographic variables that were significantly correlate with focal variables:
    - orgtype
    - orglevels
    - edu
    - dirreport
    - salary
    
## Hypothesis 1
```{r}
mod1 <- lm(orgdehum ~ wbatt + orgtype + orglevels + edu + dirreport + salary + hrpractices, data = dat)
summary(mod1)
```

```{r}
mod2 <- lm(orgdehum ~ exploitatt + orgtype + orglevels + edu + dirreport + salary + hrpractices, data = dat)
summary(mod2)
```

## Hypothesis 2
```{r}
mod3 <- lm(orgdehum ~ sblm + orgtype + orglevels + edu + dirreport + salary + hrpractices, data = dat)
summary(mod3)
```

## Hypothesis 3
```{r}
mod4 <- lm(exploitatt ~ sblm + orgtype + orglevels + edu + dirreport + salary + hrpractices, data = dat)
summary(mod4)
```

```{r}
mod5 <- lm(wbatt ~ sblm + orgtype + orglevels + edu + dirreport + salary + hrpractices, data = dat)
summary(mod5)
```

## Hypothesis 4
```{r}
print(mediate(orgdehum ~ sblm + orgtype + orglevels + edu + dirreport + salary + hrpractices + (exploitatt), data = dat, n.iter = 10000, zero = TRUE), short = FALSE)
```

## All Predictors
```{r}
mod6 <- lm(orgdehum ~ sblm + exploitatt + wbatt + orgtype + orglevels + edu + dirreport + salary + hrpractices, data = dat)
summary(mod6)
```

# CFA of Core Constructs
## Single Factor
```{r}
cfa.model <- '
  # measurement model
    factor =~ sblm_1 + sblm_2 + sblm_3 + sblm_4 + exploit_1 + exploit_2 + exploit_3 + wbatt_1 + wbatt_2 + wbatt_3 + orgdehum_1 + orgdehum_2 + orgdehum_3 + orgdehum_4 + orgdehum_5 + orgdehum_6 + orgdehum_7 + orgdehum_8 + orgdehum_9 + orgdehum_10 + orgdehum_11
'
cfa.fit <- cfa(cfa.model, data = dat)
summary(cfa.fit, fit.measures = TRUE, standardized = TRUE)
```

* Poor fit

```{r}
semPaths(cfa.fit, what = "paths", whatLabels = "std")
```

## Two Factor
```{r}
cfa.model <- '
  # measurement model
    factor1 =~ sblm_1 + sblm_2 + sblm_3 + sblm_4 + exploit_1 + exploit_2 + exploit_3 + orgdehum_1 + orgdehum_2 + orgdehum_3 + orgdehum_4 + orgdehum_5 + orgdehum_6 + orgdehum_7 + orgdehum_8 + orgdehum_9 + orgdehum_10 + orgdehum_11
    factor2 =~ wbatt_1 + wbatt_2 + wbatt_3
'
cfa.fit <- cfa(cfa.model, data = dat, estimator = "MLR")
summary(cfa.fit, fit.measures = TRUE, standardized = TRUE)
```

* Poor fit

```{r}
semPaths(cfa.fit, what = "paths", whatLabels = "std")
```

## First Order Factors
```{r}
cfa.model <- '
  # measurement model
    sblm =~ sblm_1 + sblm_2 + sblm_3 + sblm_4
    exploitatt =~ exploit_1 + exploit_2 + exploit_3
    wbatt =~ wbatt_1 + wbatt_2 + wbatt_3
    orgdehum =~ orgdehum_1 + orgdehum_2 + orgdehum_3 + orgdehum_4 + orgdehum_5 + orgdehum_6 + orgdehum_7 + orgdehum_8 + orgdehum_9 + orgdehum_10 + orgdehum_11
'
cfa.fit <- cfa(cfa.model, data = dat, estimator = "MLR")
summary(cfa.fit, fit.measures = TRUE, standardized = TRUE)
```


```{r}
semPaths(cfa.fit, what = "paths", whatLabels = "std")
```

* Better Fit

## Second Order Factor
```{r}
cfa.model <- '
  # measurement model
    latent =~ sblm + exploitatt + wbatt + orgdehum
    sblm =~ sblm_1 + sblm_2 + sblm_3 + sblm_4
    exploitatt =~ exploit_1 + exploit_2 + exploit_3
    wbatt =~ wbatt_1 + wbatt_2 + wbatt_3
    orgdehum =~ orgdehum_1 + orgdehum_2 + orgdehum_3 + orgdehum_4 + orgdehum_5 + orgdehum_6 + orgdehum_7 + orgdehum_8 + orgdehum_9 + orgdehum_10 + orgdehum_11
'
cfa.fit <- cfa(cfa.model, data = dat, estimator = "MLR")
summary(cfa.fit, fit.measures = TRUE, standardized = TRUE)
```

```{r}
semPaths(cfa.fit, what = "paths", whatLabels = "std")
```

## Second Order Factors (Separate WBATT)
```{r}
cfa.model <- '
  # measurement model
    latent1 =~ sblm + exploitatt + orgdehum
    latent2 =~ wbatt
    sblm =~ sblm_1 + sblm_2 + sblm_3 + sblm_4
    exploitatt =~ exploit_1 + exploit_2 + exploit_3
    wbatt =~ wbatt_1 + wbatt_2 + wbatt_3
    orgdehum =~ orgdehum_1 + orgdehum_2 + orgdehum_3 + orgdehum_4 + orgdehum_5 + orgdehum_6 + orgdehum_7 + orgdehum_8 + orgdehum_9 + orgdehum_10 + orgdehum_11
'
cfa.fit <- cfa(cfa.model, data = dat, estimator = "MLR")
summary(cfa.fit, fit.measures = TRUE, standardized = TRUE)
```

****

# Supplemental Analyses: SOE Further Investigation

## SOE Factur Structure

For some reason, SOE is positively related to employee-centric attributions and negatively related to organization-centric attributions and organizational dehumanization itself. 

Perhaps this is due to the distinct positive tone of certain items?

```{r}
soe.model1f <- 'soe =~ soe_1 + soe_2 + soe_3 + soe_4 + soe_5 + soe_6 + soe_7 + soe_8 + soe_9'

soe.fit1f <- cfa(soe.model1f, data = dat)
summary(soe.fit1f, fit.measures = TRUE)
```

One-factor model shows poor fit.

### EFA of SOE items
```{r}
library(nFactors)
soe.df <- dat %>%
  dplyr::select(soe_1:soe_9)
ev <- eigen(cor(soe.df)) # get eigenvalues
ap <- parallel(subject = nrow(soe.df), var = ncol(soe.df),
  rep = 100, cent = .05)
nS <- nScree(x = ev$values, aparallel = ap$eigen$qevpea)
plotnScree(nS)
```

Scree plot suggests 2 factors. 

```{r}
fa(soe.df, 2) # default: rotation = oblimin, extraction = minimum residual
```

EFA suggests that first four items load as one factor. Item 7 does not load well on the second factor.

### CFA with Two Factors
```{r}
soe.model2f <- 'soe1 =~ soe_1 + soe_2 + soe_3 + soe_4
soe2 =~ soe_5 + soe_6 + soe_7 + soe_8 + soe_9'

soe.fit2f <- cfa(soe.model2f, data = dat)
summary(soe.fit2f, fit.measures = TRUE)
```

Fit is improved compared to the one-factor solution.

### Reliability of Separate SOE Scales
```{r}
dat %>%
  dplyr::select(soe_1:soe_4) %>%
  psych::alpha(.)
```

```{r}
dat %>%
  dplyr::select(soe_5, soe_6, soe_7, soe_8, soe_9) %>%
  psych::alpha(.)
```


## Retest moderation hypotheses with different SOE items

First, load relevant libraries and supplemental dataset.
```{r}
library(effects)
library(ggplot2)

rm(dat)
dat <- read_xlsx("./Dissertation Data/dissertationdataSUPPLEMENTAL.xlsx")
```

### Correlations

```{r}
library(Hmisc)
dat %>%
  dplyr::select(exploitatt:cwb, orgtenure:suptenure, weekhours, soe1, soe2, soe3) %>%
  as.matrix(.) %>%
  rcorr(., type = "pearson")
```

```{r}
dat %>%
  select(orgtype:orgcent, status, dirreport, salary, gender, age, english, edu, racenum,
         exploitatt:cwb, soe1, soe2, soe3) %>%
  as.matrix(.) %>%
  rcorr(., type = "spearman")
```

### Hypothesis 5

SOE scale with first four items
```{r}
mod5x <- lm(orgdehum ~ sblmc*soe1c, data = dat)
summary(mod5x)
```

```{r}
inter.sd <- effect(c("sblmc*soe1c"), mod5x,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe1c = c(-sd(dat$soe1c), +sd(dat$soe1c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe1c,
              levels = c(-sd(dat$soe1c), sd(dat$soe1c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Organizational Dehumanization") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```


SOE scale with last five items
```{r}
mod5y <- lm(orgdehum ~ sblmc*soe2c, data = dat)
summary(mod5y)
```

```{r}
inter.sd <- effect(c("sblmc*soe2c"), mod5y,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe2c = c(-sd(dat$soe2c), +sd(dat$soe2c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe2c,
              levels = c(-sd(dat$soe2c), sd(dat$soe2c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Organizational Dehumanization") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```

SOE scale with last four items (removing Item 7)
```{r}
mod5z <- lm(orgdehum ~ sblmc*soe3c, data = dat)
summary(mod5z)
```

```{r}
inter.sd <- effect(c("sblmc*soe3c"), mod5z,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe3c = c(-sd(dat$soe3c), +sd(dat$soe3c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe3c,
              levels = c(-sd(dat$soe3c), sd(dat$soe3c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Organizational Dehumanization") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```

Separate SOE scales appear to operate similarly, but moderation effect is more stark with the last four/five items.

### Hypothesis 6

SOE scale with first four items.

Organization-centric attributions
```{r}
mod6ax <- lm(exploitatt ~ sblmc*soe1c, data = dat)
summary(mod6ax)
```

```{r}
inter.sd <- effect(c("sblmc*soe1c"), mod6ax,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe1c = c(-sd(dat$soe1c), +sd(dat$soe1c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe1c,
              levels = c(-sd(dat$soe1c), sd(dat$soe1c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Organization-Centric Attributions") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```
Non-significant interaction.

</br>

Employee-centric attributions
```{r}
mod6bx <- lm(wbatt ~ sblmc*soe1c, data = dat)
summary(mod6bx)
```

```{r}
inter.sd <- effect(c("sblmc*soe1c"), mod6bx,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe1c = c(-sd(dat$soe1c), +sd(dat$soe1c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe1c,
              levels = c(-sd(dat$soe1c), sd(dat$soe1c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Employee-Centric Attributions") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```
Non-significant interaction.

</br>

SOE scale with last five items.

Organization-centric attributions.
```{r}
mod6ay <- lm(exploitatt ~ sblmc*soe2c, data = dat)
summary(mod6ay)
```

```{r}
inter.sd <- effect(c("sblmc*soe2c"), mod6ay,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe2c = c(-sd(dat$soe2c), +sd(dat$soe2c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe2c,
              levels = c(-sd(dat$soe2c), sd(dat$soe2c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Organization-Centric Attributions") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```
Significant interaction.

Employee-centric attributions.
```{r}
mod6by <- lm(wbatt ~ sblmc*soe2c, data = dat)
summary(mod6by)
```

```{r}
inter.sd <- effect(c("sblmc*soe2c"), mod6by,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe2c = c(-sd(dat$soe2c), +sd(dat$soe2c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe2c,
              levels = c(-sd(dat$soe2c), sd(dat$soe2c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Employee-Centric Attributions") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```
Non-significant interaction.

</br>

SOE scale with last four items (removing Item 7).

Organization-centric attributions
```{r}
mod6az <- lm(exploitatt ~ sblmc*soe3c, data = dat)
summary(mod6az)
```

```{r}
inter.sd <- effect(c("sblmc*soe3c"), mod6az,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe3c = c(-sd(dat$soe3c), +sd(dat$soe3c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe3c,
              levels = c(-sd(dat$soe3c), sd(dat$soe3c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Organization-Centric Attributions") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```

Employee-centric attributions
```{r}
mod6bz <- lm(wbatt ~ sblmc*soe3c, data = dat)
summary(mod6bz)
```

```{r}
inter.sd <- effect(c("sblmc*soe3c"), mod6bz,
                     xlevels = list(sblmc = c(-sd(dat$sblmc), +sd(dat$sblmc)),
                                  soe3c = c(-sd(dat$soe3c), +sd(dat$soe3c))))
inter.sd <- as.data.frame(inter.sd)

# Create factors of the different variables
inter.sd$sblm <- factor(inter.sd$sblmc,
                      levels = c(-sd(dat$sblmc), sd(dat$sblmc)),
                      labels = c("-1 SD SBLM", "+ 1 SD SBLM"))
                     
inter.sd$soe <- factor(inter.sd$soe3c,
              levels = c(-sd(dat$soe3c), sd(dat$soe3c)),
              labels = c("-1 SD SOE", "+1 SD SOE"))

# Plot 
ggplot(data = inter.sd, aes(x = sblm, y = fit, group = soe)) +
      geom_line(size = 1, aes(color = soe)) +
      geom_point(aes(colour = soe), size = 2) + theme_bw() +
      # geom_ribbon(aes(ymin = fit - se, ymax = fit + se), fill = "gray", alpha = .6) +
      scale_y_continuous(limits = c(1, 7), breaks = c(1:7)) +
      ylab("Employee-Centric Attributions") + 
      xlab("Supervisor Bottom-Line Mentality") + 
      ggtitle("SBLM*SOE Interaction Plot") + 
      theme_bw() + #Removes the gray background 
      theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_blank(),) + #Removes the lines 
     scale_fill_grey()
```

Major Conclusions from Exploration of SOE scales using different items

* Overall findings from hypothesis test were replicated: SOE moderates the relationship between SBLM and organizational dehumanization & organization-centric attributions, and SOE does not moderate the relationship between SBLM and employee-centric attributions. 

* However, analyses indicated that the moderation effect of SOE on the relationship between SBLM and organization-centric attributions was only observed when using the last four/five SOE items. No moderation effect was found when using the first four SOE items.

* Furthermore, the moderation effect of SOE on the relationship between SBLM and organizational dehumanizaation is stronger using the last four/five SOE items.